Case study validations of automatic bullet matching

### 2018-11-27 index.Rmd
Add subheadings back in, slightly rearrange and add "flow" text

<!-- ## Automated Processing of 3D Scans -->

In the matching algorithm proposed in \citet{aoas}, several of the features described above are combined using a random forest \citep{breiman} to produce a similarity score based on 3D topographic scans of land engraved areas (LEAs).
From each land engraved area a signature is derived using the process described in detail in \citet{aoas}:

@@

<!-- ## Statistics for Matching Aligned Signatures -->

@@

The random forest presented in \citet{aoas} is based on a combination of multiple characteristics, including cross-correlation, number of matching striae, and number of consecutively matching striae. The output of the random forest is a score between 0 and 1 representing the algorithm's assessment of the strength of the match, where scores close to 1 indicate it to be highly likely that the aligned signatures come from the same source, while low scores indicate that the aligned signatures are highly likely to originate from different lands.

<!-- ## Interpreting the Algorithm Score -->

\hh{Any of the above described features are supposed to separate between signatures from same source and different source, e.g.\ high cross-correlation values are indicative of same sourceness of two signatures, whereas  low values are more indicate of different sources. 
An automated algorithm determines a cutoff-value along the range of possible values that introduces a barrier between identification and exclusion.
}

<!-- Firearms examiners typically set the threshold for CMS at 6; this is a threshold which is conservative, as it is much more likely to exclude same-source comparisons than it is to identify different-source comparisons.  -->
This threshold system introduces a binary classification: identification or exclusion. This definition of error is more stringent than the AFTE Theory of Identification, in that it does not allow for inconclusive results. This increased rigor may increase the error rate of the model when compared to examiner error rates, but we expect that the increased information available from the 3D measurement data will compensate for this loss. A binary decision model is also easier to interpret and provides more clear-cut, definitive results.

@@

<!-- ## Identification Errors and Algorithm Evaluation -->

@@

<!-- ## Assessing Match Strength -->

Each of the scoring methods we have described is computed on a land-to-land basis. While these comparisons are useful, the question of interest typically involves   the entire physical object (e.g. all lands on a single bullet), and a conclusion on same or different source should be reached based on the evidence of all lands of the bullets.
<!--to describe the correspondence between two pieces of physical evidence.-->
<!-- \svp{In order to aggregate land-to-land match scores, we must consider the physical structure of the evidence; that is, that the sequence of lands stems from spatial information, but the numbering of each land represents the scan order and start point rather than encoding useful information. } --><!--This last bit might be redundant-->

@@

\begin{definition}{Sequence Average and its Maximum}
Let $A$ be a square real-valued matrix of dimensions $p \times p$. For the purpose of this paper, $A$ consists of scores describing the similarity between two sets of land engraved areas.
The $k$th \emph{sequence average} $SA(A, k)$ for $k = 0, ... p-1$ is defined  as 
$$SA(A, k) = \frac{1}{p} \sum_{i=1}^{p} a_{i,i \oplus k}, \text{ where } i\oplus k := \left((i + k - 1)\mod p\right) + 1.$$
The \emph{Sequence Average Maximum} \citep[SAM, ][]{sam} of square matrix $A$ of scores is defined as
$$SAM (A) = \max_{k = 1}^{p} SA(A, k).$$
\end{definition}

Note that the sequence average maximum of the correlation between lands is used in SensoComp \citep{sensofar-sam} to capture the similarity between bullets. The correlation based SAM score has also been called the 'average correlation calculated at the max phase' in \citet{chuPilotStudyAutomated2010}.

@@

Looking back at \autoref{fig:b2b}, we see that for the two bullets from the same barrel, the sequence average for 
$k=2$ is higher than the other sequence averages, and also higher than the sequence averages for the other pair of bullets shown on the right of the figure.

SAM scores allow us to define a single quantity for each pair of bullets that describes the similarity between these two bullets.

>>>>

In the matching algorithm proposed in \citet{aoas}, several features are combined using a random forest \citep{breiman} to produce a similarity score based on 3D topographic scans of land engraved areas (LEAs). \svp{In order to generate these features, some pre-processing is necessary in order to transform the 3D surface measurements into `signatures' which can be compared.}

## Automated Processing of 3D Scans
From each land engraved area a signature is derived using the process described in detail in \citet{aoas}:

@@

## Statistics for Matching Aligned Signatures

@@

<!-- I really think this belongs in this section: it's discussing cross-correlation as a scoring statistic, rather than as a convenient way to align signatures so that scoring stats can be calculated. -->

The random forest presented in \citet{aoas} is based on a combination of multiple characteristics, including cross-correlation, number of matching striae, and number of consecutively matching striae. The output of the random forest is a score between 0 and 1 representing the algorithm's assessment of the strength of the match, where scores close to 1 indicate it to be highly likely that the aligned signatures come from the same source, while scores close to 0 indicate that the aligned signatures are highly likely to originate from different sources.

## Interpreting the Algorithm Score

\svp{The features described above are each individually designed to separate same-source and different-source signatures: for instance, same-source signatures would have high cross-correlation values and different-source signatures would have low cross-correlation values. An automated algorithm selects a cutoff value, introducing a barrier between identification and exclusion.} 
<!-- rephrased? trying to get rid of "supposed" and "same sourceness" :-p

\hh{Any of the above described features are supposed to separate between signatures from same source and different source, e.g.\ high cross-correlation values are indicative of same sourceness of two signatures, whereas  low values are more indicate of different sources. 
An automated algorithm determines a cutoff-value along the range of possible values that introduces a barrier between identification and exclusion.
}
-->

<!-- Firearms examiners typically set the threshold for CMS at 6; this is a threshold which is conservative, as it is much more likely to exclude same-source comparisons than it is to identify different-source comparisons.  -->

This threshold system introduces a binary classification: identification or exclusion. This definition of error is more stringent than the AFTE Theory of Identification, in that it does not allow for inconclusive results. This increased rigor may increase the error rate of the model when compared to examiner error rates, but we expect that the increased information available from the 3D measurement data will compensate for this loss. A binary decision model is also easier to interpret and provides more clear-cut, definitive results.

@@

## Identification Errors and Algorithm Evaluation

@@

## Assessing Bullet-to-Bullet Match Strength

Each of the scoring methods we have described is computed on a land-to-land basis. While these comparisons are useful, the question of interest typically involves the entire physical object (e.g. all lands on a single bullet), and a conclusion on same or different source should be reached based on the evidence of all lands of the bullets.

@@

\begin{definition}{Sequence Average and its Maximum}
Let $A$ be a square real-valued matrix of dimensions $p \times p$. For the purpose of this paper, $A$ consists of scores describing the similarity between two sets of land engraved areas.
The $k$th \emph{sequence average} $SA(A, k)$ for $k = 0, ... p-1$ is defined  as 
$$SA(A, k) = \frac{1}{p} \sum_{i=1}^{p} a_{i,i \oplus k}, \text{ where } i\oplus k := \left((i + k - 1)\mod p\right) + 1.$$
The \emph{Sequence Average Maximum} \citep[SAM, ][]{sam} of square matrix $A$ of scores is defined as
$$SAM (A) = \max_{k = 1}^{p} SA(A, k).$$
\end{definition}
\svp{XXX Rearranged this slightly XXX}
Looking back at \autoref{fig:b2b}, we see that for the two bullets from the same barrel, the sequence average for 
$k=2$ is higher than the other sequence averages, and also higher than the sequence averages for the other pair of bullets shown on the right of the figure. SAM scores allow us to define a single quantity for each pair of bullets that describes the similarity between these two bullets.

The sequence average maximum of the correlation between lands is used in SensoComp \citep{sensofar-sam} to capture the similarity between bullets. The correlation based SAM score has also been called the 'average correlation calculated at the max phase' in \citet{chuPilotStudyAutomated2010}.

@@
